\act{An AI-generated first act}
\BlockStageDirection{The stage is set up as a typical living room. There is a couch, a coffee table, and a TV. The TV is on, and the couch is occupied}

\scene{First Scene}{What a loving relationship}
\character{doe} \InlineStageDirection{enters the living room} Hey, Jane, what are you watching?
\character{smith} \InlineStageDirection{without looking away from the TV} Oh, just some show about a guy who can talk to animals. It's pretty funny.
\character{doe} \InlineStageDirection{walks over to the couch and sits down} Oh, that sounds interesting. What's it called?
\character{smith} \InlineStageDirection{still not looking away from the TV} I think it's called "The Animal Whisperer" or something like that. It's on every Tuesday night.
\BlockStageDirection{The TV show ends, and the screen goes black}
\characterss{doe}{smith} Huh.
\character{doe} \InlineStageDirection{stands up} Well, I'm going to bed. Good night, Jane.
\character{smith} \InlineStageDirection{finally looking away from the TV} Good night, John.

\scene{Second Scene}{A new day}
\character{doe} \InlineStageDirection{enters the living room} Good morning, Jane. Did you sleep well?
\character{smith} \InlineStageDirection{yawning} Yeah, I did. How about you?
\character{doe} \InlineStageDirection{stretching} I slept like a log. I feel great.
\character{smith} \InlineStageDirection{stands up} Well, I'm going to make some breakfast. Do you want anything?
\character{doe} \InlineStageDirection{sitting down} No, I'm good. Thanks, though.
\character{smith} \InlineStageDirection{walks into the kitchen} Okay, I'll be right back.
\character{doe} \InlineStageDirection{to himself} I'm so lucky to have Jane in my life. She's the best thing that ever happened to me.
\character{smith} \InlineStageDirection{from the kitchen} What was that, John?
\character{doe} \InlineStageDirection{smiling} Nothing, Jane. Just thinking out loud.

\scene{Third Scene}{A surprise visitor}
\character{jack} \InlineStageDirection{enters the living room} Hey, guys. What's up?
\characterss{doe}{smith} \InlineStageDirection{surprised} Jack! What are you doing here?
\character{jack} \InlineStageDirection{smiling} I was in the neighborhood, so I thought I'd drop by and say hi.
\character{doe} \InlineStageDirection{standing up} Well, it's great to see you, Jack. How have you been?
\character{jack} \InlineStageDirection{sitting down} I've been good. Just working on some new projects.
\character{smith} Oh cool, what kind of projects?
\character{jack} \InlineStageDirection{excitedly} I'm working on a new app that's going to revolutionize the way we communicate.
\character{doe} \InlineStageDirection{impressed} That sounds amazing, Jack. I can't wait to see it.
\character{jack} \InlineStageDirection{smiling} Thanks, John. I'll be sure to show it to you when it's ready.
